---
title: "Using the GEOexplorer Package"
author: "Guy Hunt"
date: "July 07, 2021"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction
GEOexplorer is a Shiny app that enables exploratory data
analysis and differential gene expression analysis to be
performed on  microarray gene expression  datasets held 
in the GEO database. The outputs are both non-interactive and
interactive visualisations which enable users to explore the
results. The development of GEOexplorer was made 
possible because of the excellent code provided by GEO2R
(https: //www.ncbi.nlm.nih.gov/geo/geo2r/).

# Installation
```{r eval=FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("GEOexplorer")
```

Or GEOexplorer can be installed from GitHub
```{r eval=FALSE}
if (!requireNamespace("devtools", quietly = TRUE))
  install.packages("devtools")

devtools::install_github("guypwhunt/GEOexplorer")
```

# Getting Started using GEOexplorer Shiny App

Getting started with the GEOexplorer Shiny App is relatively
easy and can be performed in a number of steps.

Step 1: Load the package
```{r loadLibrary}
library(GEOexplorer)
```

Step 2: Launch the shiny app in a browser.
```{r}
loadApp()
```

# Conclusion

The GEOexplorer package provides an easy way to perform 
exploratory data analysis and differential gene expression 
analysis on microarray gene expression data sets and provide 
the outputs as interactive and non-interacive visulisations.

# Reporting problems or bugs

If you run into problems using GEOquery, the 
[Bioconductor Support site](https://support.bioconductor.org/) 
is a good first place to ask for help. 
If you are convinced that there is a bug in GEOquery 
(this is pretty unusual, but not unheard of), feel free 
to submit an issue on the 
[GEOexplorer github site](https://github.com/guypwhunt/GEOexplorer).

# Session info

The following package and versions were used in the 
production of this vignette.

```{r echo=FALSE}
sessionInfo()
```
